### 2022-06-27 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@890e7b3f2b398279abf2c9d6ada1b51469df2d43 🚀

To next represent phylogeography of betacoronaviruses in bats, we
aggregated and analyzed betacoronavirus sequence data. We used the
following query to pull all \emph{Betacoronavirus} sequence data from
the GenBank Nucleotide database except SARS-CoV-2;
(``Betacoronavirus''{[}Organism{]} OR betacoronavirus{[}All Fields{]})
NOT (``Severe acute respiratory syndrome coronavirus 2''{[}Organism{]}
OR sars-cov-2{[}All Fields{]}). We added a single representative
sequence for SARS-CoV-2 and manually curated to remove sequences without
the RNA-dependent RNA polymerase (RdRp) sequence or that contained words
indicating recombinant or laboratory strains including ``patent'',
``mutant'', ``GFP'', and ``recombinant''. We filtered over-represented
taxa including betacoronavirus 1, hCoV-OC43, Middle East respiratory
syndrome coronavirus, Murine hepatitis virus, and hCoV-HKU1. Curated
betacoronavirus RdRp sequences were then aligned using
MAFFT\textsuperscript{67} v1.4.0 (Algorithm FFT-NS-2, Scoring matrix
200PAM / k=2, gap open penalty 1.53m offset value 0.123) and a maximum
likelihood tree reconstructed in IQ-TREE\textsuperscript{68} v1.6.12
with ModelFinder\textsuperscript{69} ultrafast bootstrap
approximation\textsuperscript{70} with a general time reversible model
with empirical base frequencies and the 5-discrete-rate-category
FreeRaye model of nucleotide substitution (GTR+F+R5).

We first tested the hypothesis that hotspots of viral diversification
would track hotspots of bat diversification. To do so, we plotted the
number of known bat hosts (specifically only those included in the
phylogeny, so there was a 1:1 correspondence between data sources)
against the ``mean evolutionary distinctiveness'' of the associated
viruses. To calculate this, we derived the fair proportions evolutionary
distinctiveness\textsuperscript{71} for each of the viruses in the tree,
then averaged these at the bat species level, projected these values
onto their geographic distributions, and averaged across every bat found
in a given pixel. As such, this can be thought of as a map of the mean
evolutionary distinctiveness of the known viral community believed to be
associated with a particular subset of bats present.

@@

\leavevmode\hypertarget{ref-Drexler2014EcoEvo}{}%
\CSLLeftMargin{13. }
\CSLRightInline{Drexler, J. F., Corman, V. M. \& Drosten, C. Ecology,
evolution and classification of bat coronaviruses in the aftermath of
SARS. \emph{Antiviral Research} \textbf{101}, 45--56 (2014).}

\leavevmode\hypertarget{ref-Calisher2006BatImp}{}%
\CSLLeftMargin{14. }
\CSLRightInline{Calisher, C. H., Childs, J. E., Field, H. E., Holmes, K.
V. \& Schountz, T. Bats: Important Reservoir Hosts of Emerging Viruses.
\emph{Clinical Microbiology Reviews} \textbf{19}, 531--545 (2006).}

\leavevmode\hypertarget{ref-Moratelli2015BatZoo}{}%
\CSLLeftMargin{15. }
\CSLRightInline{Moratelli, R. \& Calisher, C. H. Bats and zoonotic
viruses: Can we confidently link bats with emerging deadly viruses?
\emph{Memórias do Instituto Oswaldo Cruz} \textbf{110}, 1--22 (2015).}

\leavevmode\hypertarget{ref-Mollentze2020VirZoo}{}%
\CSLLeftMargin{16. }
\CSLRightInline{Mollentze, N. \& Streicker, D. G. Viral zoonotic risk is
homogenous among taxonomic orders of mammalian and avian reservoir
hosts. \emph{Proceedings of the National Academy of Sciences}
\textbf{117}, 9423--9430 (2020).}

\leavevmode\hypertarget{ref-Carlson2022CliCha}{}%
\CSLLeftMargin{17. }
\CSLRightInline{Carlson, C. J. \emph{et al.} Climate change increases
cross-species viral transmission risk. \emph{Nature} 1--1 (2022)
doi:\href{https://doi.org/10.1038/s41586-022-04788-w}{10.1038/s41586-022-04788-w}.}

\leavevmode\hypertarget{ref-Springer2013PhyBat}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Springer, M. S. Phylogenetics: Bats United, Microbats
Divided. \emph{Current Biology} \textbf{23}, R999--R1001 (2013).}

\leavevmode\hypertarget{ref-Teeling2005MolPhy}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Teeling, E. C. \emph{et al.} A Molecular Phylogeny for
Bats Illuminates Biogeography and the Fossil Record. \emph{Science (New
York, N.Y.)} \textbf{307}, 580--584 (2005).}

\leavevmode\hypertarget{ref-Villalobos2010DivFie}{}%
\CSLLeftMargin{20. }
\CSLRightInline{Villalobos, F. \& Arita, H. T. The diversity field of
New World leaf-nosed bats (Phyllostomidae). \emph{Global Ecology and
Biogeography} \textbf{19}, 200--211 (2010).}

\leavevmode\hypertarget{ref-Becker2022OptPre}{}%
\CSLLeftMargin{21. }
\CSLRightInline{Becker, D. J. \emph{et al.} Optimising predictive models
to prioritise viral discovery in zoonotic reservoirs. \emph{The Lancet
Microbe} (2022)
doi:\href{https://doi.org/10.1016/S2666-5247(21)00245-7}{10.1016/S2666-5247(21)00245-7}.}

\leavevmode\hypertarget{ref-Allen2017GloHot}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Allen, T. \emph{et al.} Global hotspots and correlates
of emerging zoonotic diseases. \emph{Nature Communications} \textbf{8},
(2017).}

\leavevmode\hypertarget{ref-Olival2017HosVir}{}%
\CSLLeftMargin{23. }
\CSLRightInline{Olival, K. J. \emph{et al.} Host and viral traits
predict zoonotic spillover from mammals. \emph{Nature} \textbf{546},
646--650 (2017).}

\leavevmode\hypertarget{ref-VanBrussel2022ZooDis}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Van Brussel, K. \& Holmes, E. C. Zoonotic disease and
virome diversity in bats. \emph{Current Opinion in Virology}
\textbf{52}, 192--202 (2022).}

\leavevmode\hypertarget{ref-Letko2020BatVir}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Letko, M., Seifert, S. N., Olival, K. J., Plowright, R.
K. \& Munster, V. J. Bat-borne virus diversity, spillover and emergence.
\emph{Nature Reviews Microbiology} \textbf{18}, 461--471 (2020).}

\leavevmode\hypertarget{ref-Banerjee2020NovIns}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Banerjee, A. \emph{et al.} Novel Insights Into Immune
Systems of Bats. \emph{Frontiers in Immunology} \textbf{11}, 26 (2020).}

\leavevmode\hypertarget{ref-Gorbunova2020WorGoe}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Gorbunova, V., Seluanov, A. \& Kennedy, B. K. The World
Goes Bats: Living Longer and Tolerating Viruses. \emph{Cell Metabolism}
\textbf{32}, 31--43 (2020).}

\leavevmode\hypertarget{ref-Irving2021LesHos}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Irving, A. T., Ahn, M., Goh, G., Anderson, D. E. \&
Wang, L.-F. Lessons from the host defences of bats, a unique viral
reservoir. \emph{Nature} \textbf{589}, 363--370 (2021).}

\leavevmode\hypertarget{ref-Jebb2020SixRef}{}%
\CSLLeftMargin{29. }
\CSLRightInline{Jebb, D. \emph{et al.} Six reference-quality genomes
reveal evolution of bat adaptations. \emph{Nature} \textbf{583},
578--584 (2020).}

\leavevmode\hypertarget{ref-MorenoSantillan2021LarGen}{}%
\CSLLeftMargin{30. }
\CSLRightInline{Moreno Santillán, D. D. \emph{et al.} Large-scale genome
sampling reveals unique immunity and metabolic adaptations in bats.
\emph{Molecular Ecology} mec.16027 (2021)
doi:\href{https://doi.org/10.1111/mec.16027}{10.1111/mec.16027}.}

\leavevmode\hypertarget{ref-Muylaert2022PreFut}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Muylaert, R. L. \emph{et al.} Present and future
distribution of bat hosts of sarbecoviruses: Implications for
conservation and public health. \emph{Proceedings of the Royal Society
B: Biological Sciences} \textbf{289}, 20220397 (2022).}

\leavevmode\hypertarget{ref-Wang2018SerEvi}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Wang, N. \emph{et al.} Serological Evidence of Bat
SARS-Related Coronavirus Infection in Humans, China. \emph{Virologica
Sinica} \textbf{33}, 104--107 (2018).}

\leavevmode\hypertarget{ref-Ramshaw2019DatGeo}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Ramshaw, R. E. \emph{et al.} A database of geopositioned
Middle East Respiratory Syndrome Coronavirus occurrences.
\emph{Scientific Data} \textbf{6}, 318 (2019).}

\leavevmode\hypertarget{ref-Lednicky2021IsoNov}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Lednicky, J. A. \emph{et al.} Isolation of a Novel
Recombinant Canine Coronavirus from a Visitor to Haiti: Further Evidence
of Transmission of Coronaviruses of Zoonotic Origin to Humans.
\emph{Clinical Infectious Diseases: An Official Publication of the
Infectious Diseases Society of America} ciab924 (2021)
doi:\href{https://doi.org/10.1093/cid/ciab924}{10.1093/cid/ciab924}.}

\leavevmode\hypertarget{ref-Vlasova2022AniAlp}{}%
\CSLLeftMargin{35. }
\CSLRightInline{Vlasova, A. N. \emph{et al.} Animal alphacoronaviruses
found in human patients with acute respiratory illness in different
countries. \emph{Emerging Microbes \& Infections} \textbf{11}, 699--702
(2022).}

\leavevmode\hypertarget{ref-Shi2014DeeDiv}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Shi, J. J. \emph{et al.} A Deep Divergence Time between
Sister Species of Eidolon (Pteropodidae) with Evidence for Widespread
Panmixia. \emph{Acta Chiropterologica} \textbf{16}, 279--292 (2014).}

\leavevmode\hypertarget{ref-Kettenburg2022FulGen}{}%
\CSLLeftMargin{37. }
\CSLRightInline{Kettenburg, G. \emph{et al.} Full Genome Nobecovirus
Sequences From Malagasy Fruit Bats Define a Unique Evolutionary History
for This Coronavirus Clade. \emph{Frontiers in Public Health}
\textbf{10}, (2022).}

\leavevmode\hypertarget{ref-Hazarie2021IntPop}{}%
\CSLLeftMargin{38. }
\CSLRightInline{Hazarie, S., Soriano-Paños, D., Arenas, A.,
Gómez-Gardeñes, J. \& Ghoshal, G. Interplay between population density
and mobility in determining the spread of epidemics in cities.
\emph{Communications Physics} \textbf{4}, 191 (2021).}

\leavevmode\hypertarget{ref-Xu2004EpiClu}{}%
\CSLLeftMargin{39. }
\CSLRightInline{Xu, R.-H. \emph{et al.} Epidemiologic Clues to SARS
Origin in China. \emph{Emerging Infectious Diseases} \textbf{10},
1030--1037 (2004).}

\leavevmode\hypertarget{ref-Cohen2022SamStr}{}%
\CSLLeftMargin{40. }
\CSLRightInline{Cohen, L. E., Fagre, A. C., Chen, B., Carlson, C. J. \&
Becker, D. J. Sampling strategies and pre-pandemic surveillance gaps for
bat coronaviruses. 2022.06.15.496296 (2022)
doi:\href{https://doi.org/10.1101/2022.06.15.496296}{10.1101/2022.06.15.496296}.}

\leavevmode\hypertarget{ref-Peixoto2018SynEco}{}%
\CSLLeftMargin{41. }
\CSLRightInline{Peixoto, F. P., Braga, P. H. P. \& Mendes, P. A
synthesis of ecological and evolutionary determinants of bat diversity
across spatial scales. \emph{BMC ecology} \textbf{18}, 18 (2018).}

\leavevmode\hypertarget{ref-Simmons2020BatSpe}{}%
\CSLLeftMargin{42. }
\CSLRightInline{Simmons, N. B. \& Cirranello, A. L. Bat Species of the
World: A taxonomic and geographic database. \url{https://batnames.org/}
(2020).}

\leavevmode\hypertarget{ref-Kasso2013EcoEco}{}%
\CSLLeftMargin{43. }
\CSLRightInline{Kasso, M. \& Balakrishnan, M. Ecological and Economic
Importance of Bats (Order Chiroptera). \emph{ISRN Biodiversity}
\textbf{2013}, e187415 (2013).}

\leavevmode\hypertarget{ref-Mello2011MisPar}{}%
\CSLLeftMargin{44. }
\CSLRightInline{Mello, M. A. R. \emph{et al.} The Missing Part of Seed
Dispersal Networks: Structure and Robustness of Bat-Fruit Interactions.
\emph{PLOS ONE} \textbf{6}, e17395 (2011).}

\leavevmode\hypertarget{ref-Voigt2016BatAnt}{}%
\CSLLeftMargin{45. }
\CSLRightInline{\emph{Bats in the Anthropocene: Conservation of Bats in
a Changing World}. (Springer International Publishing, 2016).
doi:\href{https://doi.org/10.1007/978-3-319-25220-9}{10.1007/978-3-319-25220-9}.}

\leavevmode\hypertarget{ref-Williams-Guillen2008BatLim}{}%
\CSLLeftMargin{46. }
\CSLRightInline{Williams-Guillén, K., Perfecto, I. \& Vandermeer, J.
Bats Limit Insects in a Neotropical Agroforestry System. \emph{Science}
\textbf{320}, 70--70 (2008).}

\leavevmode\hypertarget{ref-Gonsalves2013MosCon}{}%
\CSLLeftMargin{47. }
\CSLRightInline{Gonsalves, L., Bicknell, B., Law, B., Webb, C. \&
Monamy, V. Mosquito Consumption by Insectivorous Bats: Does Size Matter?
\emph{PLOS ONE} \textbf{8}, e77183 (2013).}

\leavevmode\hypertarget{ref-Gonsalves2013MosInf}{}%
\CSLLeftMargin{48. }
\CSLRightInline{Gonsalves, L., Lamb, S., Webb, C., Law, B. \& Monamy, V.
Do mosquitoes influence bat activity in coastal habitats? \emph{Wildlife
Research} \textbf{40}, 10--24 (2013).}

\leavevmode\hypertarget{ref-Latinne2020OriCro}{}%
\CSLLeftMargin{49. }
\CSLRightInline{Latinne, A. \emph{et al.} Origin and cross-species
transmission of bat coronaviruses in China. \emph{bioRxiv: The Preprint
Server for Biology} 2020.05.31.116061 (2020)
doi:\href{https://doi.org/10.1101/2020.05.31.116061}{10.1101/2020.05.31.116061}.}

\leavevmode\hypertarget{ref-Wu2021ComSur}{}%
\CSLLeftMargin{50. }
\CSLRightInline{Wu, Z. \emph{et al.} \emph{A comprehensive survey of bat
sarbecoviruses across China for the origin tracing of SARS-CoV and
SARS-CoV-2}. (2021)
doi:\href{https://doi.org/10.21203/rs.3.rs-885194/v1}{10.21203/rs.3.rs-885194/v1}.}

\leavevmode\hypertarget{ref-Alves2018GeoVar}{}%
\CSLLeftMargin{51. }
\CSLRightInline{Alves, D. M. C. C., Diniz-Filho, J. A. F., da Silva e
Souza, K., Gouveia, S. F. \& Villalobos, F. Geographic variation in the
relationship between large-scale environmental determinants and bat
species richness. \emph{Basic and Applied Ecology} \textbf{27}, 1--8
(2018).}

\leavevmode\hypertarget{ref-Treitler2016EffLoc}{}%
\CSLLeftMargin{52. }
\CSLRightInline{Treitler, J. T., Heim, O., Tschapka, M. \& Jung, K. The
effect of local land use and loss of forests on bats and nocturnal
insects. \emph{Ecology and Evolution} \textbf{6}, 4289--4297 (2016).}

\leavevmode\hypertarget{ref-Johnson2020GloShi}{}%
\CSLLeftMargin{53. }
\CSLRightInline{Johnson, C. K. \emph{et al.} Global shifts in mammalian
population trends reveal key predictors of virus spillover risk.
\emph{Proceedings of the Royal Society B: Biological Sciences}
\textbf{287}, 20192736 (2020).}

\leavevmode\hypertarget{ref-Gryseels2017WheVir}{}%
\CSLLeftMargin{54. }
\CSLRightInline{Gryseels, S. \emph{et al.} When Viruses Don't Go Viral:
The Importance of Host Phylogeographic Structure in the Spatial Spread
of Arenaviruses. \emph{PLOS Pathogens} \textbf{13}, e1006073 (2017).}

\leavevmode\hypertarget{ref-Amman2011InvRol}{}%
\CSLLeftMargin{55. }
\CSLRightInline{Amman, B. R. \emph{et al.} \emph{Investigating the role
of bats in emerging zoonoses: Balancing ecology, conservation and public
health interest}. (FAO, 2011).}

\leavevmode\hypertarget{ref-IUCN2021IucRed}{}%
\CSLLeftMargin{56. }
\CSLRightInline{IUCN. The IUCN Red List of Threatened Species.
\url{https://www.iucnredlist.org} (2021).}

>>>>

To next represent phylogeography of betacoronaviruses in bats, we
aggregated and analyzed betacoronavirus sequence data. We used the
following query to pull all \emph{Betacoronavirus} sequence data from
the GenBank Nucleotide database except SARS-CoV-2;
(``Betacoronavirus''{[}Organism{]} OR betacoronavirus{[}All Fields{]})
NOT (``Severe acute respiratory syndrome coronavirus 2''{[}Organism{]}
OR sars-cov-2{[}All Fields{]}). We added a single representative
sequence for SARS-CoV-2 and manually curated to remove sequences without
the RNA-dependent RNA polymerase (RdRp) sequence or that contained words
indicating recombinant or laboratory strains including ``patent'',
``mutant'', ``GFP'', and ``recombinant''. We filtered over-represented
taxa including betacoronavirus 1, hCoV-OC43, Middle East respiratory
syndrome coronavirus, Murine hepatitis virus, and hCoV-HKU1. Curated
betacoronavirus RdRp sequences were then aligned using
MAFFT\textsuperscript{63} v1.4.0 (Algorithm FFT-NS-2, Scoring matrix
200PAM / k=2, gap open penalty 1.53m offset value 0.123) and a maximum
likelihood tree reconstructed in IQ-TREE\textsuperscript{64} v1.6.12
with ModelFinder\textsuperscript{65} ultrafast bootstrap
approximation\textsuperscript{66} with a general time reversible model
with empirical base frequencies and the 5-discrete-rate-category
FreeRaye model of nucleotide substitution (GTR+F+R5).

We first tested the hypothesis that hotspots of viral diversification
would track hotspots of bat diversification. To do so, we plotted the
number of known bat hosts (specifically only those included in the
phylogeny, so there was a 1:1 correspondence between data sources)
against the ``mean evolutionary distinctiveness'' of the associated
viruses. To calculate this, we derived the fair proportions evolutionary
distinctiveness\textsuperscript{67} for each of the viruses in the tree,
then averaged these at the bat species level, projected these values
onto their geographic distributions, and averaged across every bat found
in a given pixel. As such, this can be thought of as a map of the mean
evolutionary distinctiveness of the known viral community believed to be
associated with a particular subset of bats present.

@@

\leavevmode\hypertarget{ref-Olival2017HosVir}{}%
\CSLLeftMargin{13. }
\CSLRightInline{Olival, K. J. \emph{et al.} Host and viral traits
predict zoonotic spillover from mammals. \emph{Nature} \textbf{546},
646--650 (2017).}

\leavevmode\hypertarget{ref-Becker2022OptPre}{}%
\CSLLeftMargin{14. }
\CSLRightInline{Becker, D. J. \emph{et al.} Optimising predictive models
to prioritise viral discovery in zoonotic reservoirs. \emph{The Lancet
Microbe} (2022)
doi:\href{https://doi.org/10.1016/S2666-5247(21)00245-7}{10.1016/S2666-5247(21)00245-7}.}

\leavevmode\hypertarget{ref-Carlson2022CliCha}{}%
\CSLLeftMargin{15. }
\CSLRightInline{Carlson, C. J. \emph{et al.} Climate change increases
cross-species viral transmission risk. \emph{Nature} 1--1 (2022)
doi:\href{https://doi.org/10.1038/s41586-022-04788-w}{10.1038/s41586-022-04788-w}.}

\leavevmode\hypertarget{ref-Springer2013PhyBat}{}%
\CSLLeftMargin{16. }
\CSLRightInline{Springer, M. S. Phylogenetics: Bats United, Microbats
Divided. \emph{Current Biology} \textbf{23}, R999--R1001 (2013).}

\leavevmode\hypertarget{ref-Teeling2005MolPhy}{}%
\CSLLeftMargin{17. }
\CSLRightInline{Teeling, E. C. \emph{et al.} A Molecular Phylogeny for
Bats Illuminates Biogeography and the Fossil Record. \emph{Science (New
York, N.Y.)} \textbf{307}, 580--584 (2005).}

\leavevmode\hypertarget{ref-Villalobos2010DivFie}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Villalobos, F. \& Arita, H. T. The diversity field of
New World leaf-nosed bats (Phyllostomidae). \emph{Global Ecology and
Biogeography} \textbf{19}, 200--211 (2010).}

\leavevmode\hypertarget{ref-Allen2017GloHot}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Allen, T. \emph{et al.} Global hotspots and correlates
of emerging zoonotic diseases. \emph{Nature Communications} \textbf{8},
(2017).}

\leavevmode\hypertarget{ref-VanBrussel2022ZooDis}{}%
\CSLLeftMargin{20. }
\CSLRightInline{Van Brussel, K. \& Holmes, E. C. Zoonotic disease and
virome diversity in bats. \emph{Current Opinion in Virology}
\textbf{52}, 192--202 (2022).}

\leavevmode\hypertarget{ref-Letko2020BatVir}{}%
\CSLLeftMargin{21. }
\CSLRightInline{Letko, M., Seifert, S. N., Olival, K. J., Plowright, R.
K. \& Munster, V. J. Bat-borne virus diversity, spillover and emergence.
\emph{Nature Reviews Microbiology} \textbf{18}, 461--471 (2020).}

\leavevmode\hypertarget{ref-Banerjee2020NovIns}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Banerjee, A. \emph{et al.} Novel Insights Into Immune
Systems of Bats. \emph{Frontiers in Immunology} \textbf{11}, 26 (2020).}

\leavevmode\hypertarget{ref-Gorbunova2020WorGoe}{}%
\CSLLeftMargin{23. }
\CSLRightInline{Gorbunova, V., Seluanov, A. \& Kennedy, B. K. The World
Goes Bats: Living Longer and Tolerating Viruses. \emph{Cell Metabolism}
\textbf{32}, 31--43 (2020).}

\leavevmode\hypertarget{ref-Irving2021LesHos}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Irving, A. T., Ahn, M., Goh, G., Anderson, D. E. \&
Wang, L.-F. Lessons from the host defences of bats, a unique viral
reservoir. \emph{Nature} \textbf{589}, 363--370 (2021).}

\leavevmode\hypertarget{ref-Jebb2020SixRef}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Jebb, D. \emph{et al.} Six reference-quality genomes
reveal evolution of bat adaptations. \emph{Nature} \textbf{583},
578--584 (2020).}

\leavevmode\hypertarget{ref-MorenoSantillan2021LarGen}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Moreno Santillán, D. D. \emph{et al.} Large-scale genome
sampling reveals unique immunity and metabolic adaptations in bats.
\emph{Molecular Ecology} mec.16027 (2021)
doi:\href{https://doi.org/10.1111/mec.16027}{10.1111/mec.16027}.}

\leavevmode\hypertarget{ref-Muylaert2022PreFut}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Muylaert, R. L. \emph{et al.} Present and future
distribution of bat hosts of sarbecoviruses: Implications for
conservation and public health. \emph{Proceedings of the Royal Society
B: Biological Sciences} \textbf{289}, 20220397 (2022).}

\leavevmode\hypertarget{ref-Wang2018SerEvi}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Wang, N. \emph{et al.} Serological Evidence of Bat
SARS-Related Coronavirus Infection in Humans, China. \emph{Virologica
Sinica} \textbf{33}, 104--107 (2018).}

\leavevmode\hypertarget{ref-Ramshaw2019DatGeo}{}%
\CSLLeftMargin{29. }
\CSLRightInline{Ramshaw, R. E. \emph{et al.} A database of geopositioned
Middle East Respiratory Syndrome Coronavirus occurrences.
\emph{Scientific Data} \textbf{6}, 318 (2019).}

\leavevmode\hypertarget{ref-Lednicky2021IsoNov}{}%
\CSLLeftMargin{30. }
\CSLRightInline{Lednicky, J. A. \emph{et al.} Isolation of a Novel
Recombinant Canine Coronavirus from a Visitor to Haiti: Further Evidence
of Transmission of Coronaviruses of Zoonotic Origin to Humans.
\emph{Clinical Infectious Diseases: An Official Publication of the
Infectious Diseases Society of America} ciab924 (2021)
doi:\href{https://doi.org/10.1093/cid/ciab924}{10.1093/cid/ciab924}.}

\leavevmode\hypertarget{ref-Vlasova2022AniAlp}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Vlasova, A. N. \emph{et al.} Animal alphacoronaviruses
found in human patients with acute respiratory illness in different
countries. \emph{Emerging Microbes \& Infections} \textbf{11}, 699--702
(2022).}

\leavevmode\hypertarget{ref-Shi2014DeeDiv}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Shi, J. J. \emph{et al.} A Deep Divergence Time between
Sister Species of Eidolon (Pteropodidae) with Evidence for Widespread
Panmixia. \emph{Acta Chiropterologica} \textbf{16}, 279--292 (2014).}

\leavevmode\hypertarget{ref-Kettenburg2022FulGen}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Kettenburg, G. \emph{et al.} Full Genome Nobecovirus
Sequences From Malagasy Fruit Bats Define a Unique Evolutionary History
for This Coronavirus Clade. \emph{Frontiers in Public Health}
\textbf{10}, (2022).}

\leavevmode\hypertarget{ref-Hazarie2021IntPop}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Hazarie, S., Soriano-Paños, D., Arenas, A.,
Gómez-Gardeñes, J. \& Ghoshal, G. Interplay between population density
and mobility in determining the spread of epidemics in cities.
\emph{Communications Physics} \textbf{4}, 191 (2021).}

\leavevmode\hypertarget{ref-Xu2004EpiClu}{}%
\CSLLeftMargin{35. }
\CSLRightInline{Xu, R.-H. \emph{et al.} Epidemiologic Clues to SARS
Origin in China. \emph{Emerging Infectious Diseases} \textbf{10},
1030--1037 (2004).}

\leavevmode\hypertarget{ref-Cohen2022SamStr}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Cohen, L. E., Fagre, A. C., Chen, B., Carlson, C. J. \&
Becker, D. J. Sampling strategies and pre-pandemic surveillance gaps for
bat coronaviruses. 2022.06.15.496296 (2022)
doi:\href{https://doi.org/10.1101/2022.06.15.496296}{10.1101/2022.06.15.496296}.}

\leavevmode\hypertarget{ref-Peixoto2018SynEco}{}%
\CSLLeftMargin{37. }
\CSLRightInline{Peixoto, F. P., Braga, P. H. P. \& Mendes, P. A
synthesis of ecological and evolutionary determinants of bat diversity
across spatial scales. \emph{BMC ecology} \textbf{18}, 18 (2018).}

\leavevmode\hypertarget{ref-Simmons2020BatSpe}{}%
\CSLLeftMargin{38. }
\CSLRightInline{Simmons, N. B. \& Cirranello, A. L. Bat Species of the
World: A taxonomic and geographic database. \url{https://batnames.org/}
(2020).}

\leavevmode\hypertarget{ref-Kasso2013EcoEco}{}%
\CSLLeftMargin{39. }
\CSLRightInline{Kasso, M. \& Balakrishnan, M. Ecological and Economic
Importance of Bats (Order Chiroptera). \emph{ISRN Biodiversity}
\textbf{2013}, e187415 (2013).}

\leavevmode\hypertarget{ref-Mello2011MisPar}{}%
\CSLLeftMargin{40. }
\CSLRightInline{Mello, M. A. R. \emph{et al.} The Missing Part of Seed
Dispersal Networks: Structure and Robustness of Bat-Fruit Interactions.
\emph{PLOS ONE} \textbf{6}, e17395 (2011).}

\leavevmode\hypertarget{ref-Voigt2016BatAnt}{}%
\CSLLeftMargin{41. }
\CSLRightInline{\emph{Bats in the Anthropocene: Conservation of Bats in
a Changing World}. (Springer International Publishing, 2016).
doi:\href{https://doi.org/10.1007/978-3-319-25220-9}{10.1007/978-3-319-25220-9}.}

\leavevmode\hypertarget{ref-Williams-Guillen2008BatLim}{}%
\CSLLeftMargin{42. }
\CSLRightInline{Williams-Guillén, K., Perfecto, I. \& Vandermeer, J.
Bats Limit Insects in a Neotropical Agroforestry System. \emph{Science}
\textbf{320}, 70--70 (2008).}

\leavevmode\hypertarget{ref-Gonsalves2013MosCon}{}%
\CSLLeftMargin{43. }
\CSLRightInline{Gonsalves, L., Bicknell, B., Law, B., Webb, C. \&
Monamy, V. Mosquito Consumption by Insectivorous Bats: Does Size Matter?
\emph{PLOS ONE} \textbf{8}, e77183 (2013).}

\leavevmode\hypertarget{ref-Gonsalves2013MosInf}{}%
\CSLLeftMargin{44. }
\CSLRightInline{Gonsalves, L., Lamb, S., Webb, C., Law, B. \& Monamy, V.
Do mosquitoes influence bat activity in coastal habitats? \emph{Wildlife
Research} \textbf{40}, 10--24 (2013).}

\leavevmode\hypertarget{ref-Latinne2020OriCro}{}%
\CSLLeftMargin{45. }
\CSLRightInline{Latinne, A. \emph{et al.} Origin and cross-species
transmission of bat coronaviruses in China. \emph{bioRxiv: The Preprint
Server for Biology} 2020.05.31.116061 (2020)
doi:\href{https://doi.org/10.1101/2020.05.31.116061}{10.1101/2020.05.31.116061}.}

\leavevmode\hypertarget{ref-Wu2021ComSur}{}%
\CSLLeftMargin{46. }
\CSLRightInline{Wu, Z. \emph{et al.} \emph{A comprehensive survey of bat
sarbecoviruses across China for the origin tracing of SARS-CoV and
SARS-CoV-2}. (2021)
doi:\href{https://doi.org/10.21203/rs.3.rs-885194/v1}{10.21203/rs.3.rs-885194/v1}.}

\leavevmode\hypertarget{ref-Alves2018GeoVar}{}%
\CSLLeftMargin{47. }
\CSLRightInline{Alves, D. M. C. C., Diniz-Filho, J. A. F., da Silva e
Souza, K., Gouveia, S. F. \& Villalobos, F. Geographic variation in the
relationship between large-scale environmental determinants and bat
species richness. \emph{Basic and Applied Ecology} \textbf{27}, 1--8
(2018).}

\leavevmode\hypertarget{ref-Treitler2016EffLoc}{}%
\CSLLeftMargin{48. }
\CSLRightInline{Treitler, J. T., Heim, O., Tschapka, M. \& Jung, K. The
effect of local land use and loss of forests on bats and nocturnal
insects. \emph{Ecology and Evolution} \textbf{6}, 4289--4297 (2016).}

\leavevmode\hypertarget{ref-Johnson2020GloShi}{}%
\CSLLeftMargin{49. }
\CSLRightInline{Johnson, C. K. \emph{et al.} Global shifts in mammalian
population trends reveal key predictors of virus spillover risk.
\emph{Proceedings of the Royal Society B: Biological Sciences}
\textbf{287}, 20192736 (2020).}

\leavevmode\hypertarget{ref-Gryseels2017WheVir}{}%
\CSLLeftMargin{50. }
\CSLRightInline{Gryseels, S. \emph{et al.} When Viruses Don't Go Viral:
The Importance of Host Phylogeographic Structure in the Spatial Spread
of Arenaviruses. \emph{PLOS Pathogens} \textbf{13}, e1006073 (2017).}

\leavevmode\hypertarget{ref-Amman2011InvRol}{}%
\CSLLeftMargin{51. }
\CSLRightInline{Amman, B. R. \emph{et al.} \emph{Investigating the role
of bats in emerging zoonoses: Balancing ecology, conservation and public
health interest}. (FAO, 2011).}

\leavevmode\hypertarget{ref-IUCN2021IucRed}{}%
\CSLLeftMargin{52. }
\CSLRightInline{IUCN. The IUCN Red List of Threatened Species.
\url{https://www.iucnredlist.org} (2021).}

\leavevmode\hypertarget{ref-RouaultEven2022GdaOgr}{}%
\CSLLeftMargin{53. }
\CSLRightInline{Rouault, E. \emph{et al.} \emph{GDAL/OGR Geospatial Data
Abstraction software Library}. (Zenodo, 2022).
doi:\href{https://doi.org/10.5281/ZENODO.5884351}{10.5281/ZENODO.5884351}.}

\leavevmode\hypertarget{ref-Faith1992ConEva}{}%
\CSLLeftMargin{54. }
\CSLRightInline{Faith, D. P. Conservation evaluation and phylogenetic
diversity. \emph{Biological Conservation} \textbf{61}, 1--10 (1992).}

\leavevmode\hypertarget{ref-Upham2019InfMam}{}%
\CSLLeftMargin{55. }
\CSLRightInline{Upham, N. S., Esselstyn, J. A. \& Jetz, W. Inferring the
mammal tree: Species-level sets of phylogenies for questions in ecology,
evolution, and conservation. \emph{PLOS Biology} \textbf{17}, e3000494
(2019).}

\leavevmode\hypertarget{ref-Legendre2013BetDiv}{}%
\CSLLeftMargin{56. }
\CSLRightInline{Legendre, P. \& De Cáceres, M. Beta diversity as the
variance of community data: Dissimilarity coefficients and partitioning.
\emph{Ecology Letters} \textbf{16}, 951--963 (2013).}

\leavevmode\hypertarget{ref-Legendre2019SpaTem}{}%
\CSLLeftMargin{57. }
\CSLRightInline{Legendre, P. \& Condit, R. Spatial and temporal analysis
of beta diversity in the Barro Colorado Island forest dynamics plot,
Panama. \emph{Forest Ecosystems} \textbf{6}, 7 (2019).}
